master thesis

### 2018-03-13 Paper - Latex/Paper - Skizze - v3.tex
Paper - Results - correlation between Effects of Phyla

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & 545740 & 499227 & 482265 \\
            \hline
            multifurc $\sim$ taxa + depth & 544789 & 493017 & XXXXX \\
            \hline
            multifurc $\sim$ taxa * depth & 544062 & 488366 & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of unknown information}
        \label{table:...} 
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & \cellcolor{green!15}545799 & \cellcolor{green!35}500004 & \cellcolor{green!45}485121 \\
            \hline
            multifurc $\sim$ taxa + depth & \cellcolor{green!15}544862 & \cellcolor{green!40}493808 & \cellcolor{green!45}481869 \\
            \hline
            multifurc $\sim$ taxa * depth & \cellcolor{green!15}544179 & \cellcolor{green!45}489845 & \cellcolor{green!50}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BIC of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

@@

@@

    \begin{table}[h!]
      \begin{center}
        \begin{tabular}{ |l|l|r|r|r|r| }
          \hline
          Taxa & Model / Effects & min & max & mean & median \\
          \hline \hline
          Kingdom & globi $\sim$ taxa & 0,01 & 0,04 & 0,02 & 0,01 \\
          & globi $\sim$ taxa + depth & 0,01 & 0,03 & 0,02 & 0,01 \\
          & globi $\sim$ taxa * depth & 0,00 & 0,03 & 0,01 & 0,01 \\
          \hline
          Phylum & globi $\sim$ taxa & 0,17 & 393501,80 & 32208,79 & 6149,78 \\
          & globi $\sim$ taxa + depth & 0,32 & 567010,90 & 55149,54 & 10783,18 \\
          & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
          % \hline
          % Class & globi $\sim$ taxa & 0,10 & 628190,10 & 44684,53 & 1491,77 \\
          % & globi $\sim$ taxa + depth &  &  &  &  \\
          % & globi $\sim$ taxa * depth &  &  &  &  \\
          \hline
        \end{tabular} 
      \end{center}
      \caption{Effects of Taxa in models for unknown data}
      \label{table:Effects unknown data} 
    \end{table}

@@

>>>>

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & 545740 & \cellcolor{green!10}499227 & \cellcolor{green!30}482265 \\
            \hline
            multifurc $\sim$ taxa + depth & 544789 & \cellcolor{green!10}493017 & \cellcolor{green!50}478998 \\
            \hline
            multifurc $\sim$ taxa * depth & 544062 & \cellcolor{green!30}488366 & \cellcolor{green!50}476382 \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of unknown information}
        \label{table:...} 
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class \\
            \hline \hline
            multifurc $\sim$ taxa & 545799 & \cellcolor{green!10}500004 & \cellcolor{green!50}485121 \\
            \hline
            multifurc $\sim$ taxa + depth & 544862 & \cellcolor{green!30}493808 & \cellcolor{green!50}481869 \\
            \hline
            multifurc $\sim$ taxa * depth & 544179 & \cellcolor{green!50}489845 & \cellcolor{green!50}481494 \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BICs of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

@@

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & XXXXX & XXXXX & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117703 & XXXXX & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & 117592 & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Residuals of cross validation prediction}
        \label{table:Residuals cross validation} 
      \end{table}

@@

    \begin{table}[h!]
      \begin{center}
        \begin{tabular}{ |l|l|r|r|r|r| }
          \hline
          Taxa & Model / Effects & min & max & mean & median \\
          \hline \hline
          Kingdom & globi $\sim$ taxa         & 0,01 & 0,04 & 0,02 & 0,01 \\
                  & globi $\sim$ taxa + depth & 0,01 & 0,03 & 0,02 & 0,01 \\
                  & globi $\sim$ taxa * depth & 0,00 & 0,03 & 0,01 & 0,01 \\
          \hline
          Phylum & globi $\sim$ taxa          & 0,17 & 393501,80 & 32208,79 & 6149,78 \\
                  & globi $\sim$ taxa + depth & 0,32 & 567010,90 & 55149,54 & 10783,18 \\
                  & globi $\sim$ taxa * depth & 0,00 & 1000000,00 & 225375,33 & 2511,58 \\
          \hline
        \end{tabular} 
      \end{center}
      \caption{Effects of Taxa in models for unknown data}
      \label{table:Effects unknown data} 
    \end{table}

@@

    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 15mm, clip, width=\textwidth]{Figures/EffectsOfModel-Data-Phylum.JPG}
      \caption{Effects of Model: Data $\sim$ Phylum}
      \label{fig:...}
    \end{figure}
    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum.JPG}
      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth)}
      \label{fig:...}
    \end{figure}
    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=\textwidth]{Figures/EffectsOf3Models-Data-Phylum_loglog.JPG}
      \caption{Effects of 3 Models: Data $\sim$ Phylum (+/* depth) \\ both axis in log scale}
      \label{fig:...}
    \end{figure}
